\textsf{Are large language models superhuman chemists?}

### 2024-08-08 src/tex/appendix.tex
small fixes (typo, abbreviations) + fix incomplete citations

\subsection{Influence of model scale}
To obtain first insights in how the performance \glspl{llm} depends on scale, we tested the \glspl{llm} of the LLaMA series. 
Interestingly, we find that the 7B and 70B models perform comparably, with the 7B showing lower performance (fraction of correct answers for the 7B, 13B, and 70B models are \variable{output/llama/llama_7b.txt}, \variable{output/llama/llama_13b.txt}, \variable{output/llama/llama_70b.txt}).

>>>>

\subsection{Influence of model scale}
To obtain first insights in how the performance \glspl{llm} depends on scale, we tested the \glspl{llm} of the LLaMA series. 
Interestingly, we find that the 7B and 70B models perform comparably, with the 13B showing lower performance (fraction of correct answers for the 7B, 13B, and 70B models are \variable{output/llama/llama_7b.txt}, \variable{output/llama/llama_13b.txt}, \variable{output/llama/llama_70b.txt}).

### 2024-08-08 src/tex/ms.tex
[showyourwork]
small fixes (typo, abbreviations) + fix incomplete citations

\begin{figure}[!htb]
    \centering
    \includegraphics{figures/question_count_barplot.pdf}
    \caption{\textbf{Number of questions for different topics.} The topics have been assigned using a combination of a rule-based system (mostly based on the source the question has been sampled from) and a classifier operating on word embeddings of the questions. 
    The figure shows that not all aspects of chemistry are equally represented in our corpus. The \chembench corpus, by design, currently focuses on safety-related aspects, which is also evident in \Cref{fig:question_diversity}. This figure represents the combined count of \glstext{mcq} and open-ended questions.}
    \label{fig:topic_barplot}
    \script{plot_statistics.py}
\end{figure}

@@

\subparagraph{Instruction-tuned models} In addition, we used Claude 2, Claude3 (Opus),\autocite{anthropicClaudeModelFamily2024} GPT-4,\autocite{openai2024gpt4} GPT-3.5-turbo,\autocite{brown2020language} Gemini Pro,\autocite{gemini} Mixtral-8x7b\autocite{jiang2024mixtral} LLaMA2 (7B, 13B, 70B),\autocite{touvron2023llama} as well as the 7B chat model from Perplexity.AI.

>>>>

\begin{figure}[!htb]
    \centering
    \includegraphics{figures/question_count_barplot.pdf}
    \caption{\textbf{Number of questions for different topics.} The topics have been assigned using a combination of a rule-based system (mostly based on the source the question has been sampled from) and a classifier operating on word embeddings of the questions. 
    The figure shows that not all aspects of chemistry are equally represented in our corpus. The \chembench corpus, by design, currently focuses on safety-related aspects, which is also evident in \Cref{fig:question_diversity}. This figure represents the combined count of multiple-choice questions (\gls{mcq}) and open-ended questions.}
    \label{fig:topic_barplot}
    \script{plot_statistics.py}
\end{figure}

@@

\subparagraph{Instruction-tuned models} In addition, we used Claude 2, Claude3 (Opus),\autocite{anthropicClaudeModelFamily2024} GPT-4,\autocite{openai2024gpt4} GPT-3.5-turbo,\autocite{brown2020language} Gemini Pro,\autocite{gemini} Mixtral-8x7b,\autocite{jiang2024mixtral} LLaMA2 (7B, 13B, 70B),\autocite{touvron2023llama} as well as the 7B chat model from Perplexity.AI.
